Automated Topic Naming

### 2012-01-17 ese/ese.tex

We feel these results are poor. The aggregate view of a Kappa of
$0.1$ indicates there is some weak agreement. We found that
there was a lot of agreement in terms of lack of a tag, but often more
disagreement when a tag should be applied. After some discussion we concluded that usability was a source of
disagreement. Do user manuals improve usability? Is a command-line
option a usability issue? These kinds of questions illustrate some of
the agreement, disagreement and ambiguity about these labels. 
Thus we would recommend that future annotators make a concerted effort
to train and discuss when one applies an annotation.
%Furthermore, 
%both annotators found that the annotation was time-consuming and
%difficult.

>>>>

We feel these results are poor. The aggregate view of a Kappa of
$0.1$ indicates there is some weak agreement. We found that
there was a lot of agreement in terms of lack of a tag, but often more
disagreement when a tag should be applied. After some discussion we concluded that usability was a source of
disagreement. Do user manuals improve usability? Is a command-line
option a usability issue? These kinds of questions illustrate some of
the agreement, disagreement and ambiguity about these labels. 
Thus we would recommend that future annotators make a concerted effort
to train and discuss when one applies an annotation.

Empirically how poor were our results? We decided to compare our
results against simulated or random results. In the first simulation
we sampled with replacement from our own NFR label distributions to
produce random ratings that looked like our own. We then applied the
Kappa-statistic on this sampling versus our labelling, and repeated
this 10000 times, we found that
for 4 out of 7 NFR labels, our labels IRR were greater than the random
IRR measures 95\% of the time. For portability and efficiency, our IRR
was greater 100\% of the time both for Neil's ratings, Abram's ratings
and the union of both Neil and Abram. Figure \ref{fig:irr} depicts the IRR of
these sampled ratings versus our IRR using the Kappa statistic.

We also achieved similar results if the ratings were pulled from a
uniform distributions. What this does indicate is that our labels and
ratings were definitely better than random except for functionality,
reliability and usability.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/self-sample-Both}
  \caption{Measured IRR versus IRR of labeling random simulations.}
  \label{fig:irr}
\end{figure}
